Happiness in US: Analysis of the Effects of Demographic Factors during 1972 to 2021

### 2023-03-16 outputs/paper/Happiness-in-US-Analysis-of-the-Effects-of-Demographic-Factors-during-1972-to-2021.qmd
changed title

---
title: "Happiness in US"
subtitle: "Analysis of the Effects of Demographic Factors during 1972 to 2021"
author: 
  - Rae Zhang
  - Faustine Fan
  - Myra Li
thanks: "Code and data are available at: https://github.com/JunweiZhang130/Happiness-in-US-Analysis-of-the-Effects-of-Demographic-Factors-during-1972-to-2021.git"
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "This essay explores the trends of happiness in the United States from 1972 to 2021 and identifies the significant factors that affect happiness levels. The report is based on the data gathered in US General Social Survey, and it investigates the impact of demographic features like sex, race, marital status, education, and employment types on happiness levels. The report hypothesizes that education, social isolation, and work status have a more significant impact on happiness levels than demographic features like race and gender. The COVID-19 pandemic has had overall negative effects on happiness levels. The report concludes that understanding the roots of different levels of happiness can help policymakers and society develop effective strategies to improve the quality of life for everyone."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Happiness in US: Analysis of the Effects of Demographic Factors during 1972 to 2021"
author: 
  - Rae Zhang
  - Faustine Fan
  - Myra Li
thanks: "Code and data are available at: https://github.com/JunweiZhang130/Happiness-in-US-Analysis-of-the-Effects-of-Demographic-Factors-during-1972-to-2021.git"
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "This essay explores the trends of happiness in the United States from 1972 to 2021 and identifies the significant factors that affect happiness levels. The report is based on the data gathered in US General Social Survey, and it investigates the impact of demographic features like sex, race, marital status, education, and employment types on happiness levels. The report hypothesizes that education, social isolation, and work status have a more significant impact on happiness levels than demographic features like race and gender. The COVID-19 pandemic has had overall negative effects on happiness levels. The report concludes that understanding the roots of different levels of happiness can help policymakers and society develop effective strategies to improve the quality of life for everyone."
format: pdf
number-sections: true
bibliography: references.bib
---
